### 2015-11-30 config/glossaries.inc.tex
cleanup of LPMtrunc section

\newsymbolglos{E-approx}{\approx}{Approximately equal}
\newsymbolglos{E-bydef}{\isdef}{Equal by definition}
\newsymbolglos{E-propto}{\propto}{Proportional to}

@@

\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln \placeholder}{Natural logarithm of \placeholder}
\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when B is omitted, the decimal logarithm is implied)}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}

@@

\newacronym{IEEE}{IEEE}{Institute of Electrical and Electronics Engineers}
\newacronym{IFAC}{IFAC}{International Federation of Automatic Control}
\newacronym{iid}{i.i.d.}{independent and identically distributed}

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LTI}{LTI}{linear time-invariant}

@@

\newacronym{RFIR}{RFIR}{Regularized Finite Impulse Response}

>>>>

\newsymbolglos{E-approx}{\approx}{Is approximately equal to \ldots}
\newsymbolglos{E-bydef}{\isdef}{Is defined as \ldots}
\newsymbolglos{E-propto}{\propto}{Is proportional to \ldots}
\newsymbolglos{E-distributed}{\distributedAs}{Is distributed as \ldots}

@@

\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln \placeholder}{Natural logarithm of \placeholder}
\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when B is omitted, the decimal logarithm is implied)}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}

@@

\newacronym{IDFT}{IDFT}{inverse discrete Fourier transform}
\newacronym{IEEE}{IEEE}{Institute of Electrical and Electronics Engineers}
\newacronym{IFAC}{IFAC}{International Federation of Automatic Control}
\newacronym{iid}{i.i.d.}{independent and identically distributed}

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LS}{LS}{least-squares}
\newacronym{LTI}{LTI}{linear time-invariant}

@@

\newacronym{RFIR}{RFIR}{Regularized Finite Impulse Response}
\newacronym{RMS}{RMS}{root-mean-square}
\newacronym{RMSE}{RMSE}{root mean squared error}
